Plots_for_DOE_poster

### 2020-03-06 R/Plots_for_DOE_Poster.Rmd
Move R and Rmd files to R directory and rda files to data

library(scales)
show_col(viridis(8, option = "B"))

@@

theme_set(theme_poster)
frz_freq %>%
  filter(Loss_BRKG > 159 | Loss_LINC > 179 | Loss_FRMI > 84 | 
           Loss_CLMB > 94) %>%
  mutate(Loss_freq = (Loss_BRKG/MAC_BRKG_2018 + Loss_FRMI/MAC_FRMI_2018 +
                            Loss_LINC/MAC_LINC_2018 +
                            Loss_CLMB/MAC_CLMB_2018)/4) %>% 
  filter(Loss_freq > 0.5) %>%
  ggplot(aes(x = POS/1000000, y = Loss_freq)) +
  geom_point(aes(color = CHR), alpha = 0.35) + 
  facet_wrap(~CHR, scales = "free_x", nrow = 1) + 
  scale_fill_viridis(trans = "log10", option = "B") + 
  xlab("Position (Mb)") + ylab("Fraction of Minor Allele Lost") +
    scale_x_continuous(expand = c(0.12, 0.12)) +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = c(rep(c("#1B0C42FF", "grey"), 9)))

save_plot(filename = "Distribution_of_SNPs_1per_delta_all_four_sites_lost_50per.png", plot = last_plot(), base_asp = 4, base_height = 4)

@@

# Manhattan plots for GR50 in KBSM and biomass in TMPL
```{r}
gwas_data <- readRDS("GWAS_datatable_TMPL_BIOMASS_5_PCs.rds")
gwas_data[,FDR_adj := p.adjust(pvalue, method = "BH")]
FDRthreshhi <- gwas_data %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0.000501, 1)) %>%  # 5% FDR threshold currently.
    summarise(thresh = max(log10p))
  FDRthreshlo <- gwas_data %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0, 0.000499)) %>%  # 5% FDR threshold currently.
    summarise(thresh = min(log10p))
  if(FDRthreshhi$thresh[1] > 0 & FDRthreshlo$thresh[1] > 0){
    FDRthreshold = (FDRthreshhi$thresh[1] + FDRthreshlo$thresh[1])/2
  } else if(FDRthreshhi$thresh[1] > 0){
    FDRthreshold = FDRthreshhi$thresh[1]
  } else if(FDRthreshlo$thresh[1] > 0){
    FDRthreshold = FDRthreshlo$thresh[1]
  } else {
    FDRthreshold = NA
  }

  ggmanobject1 <- gwas_data %>%
    filter(log10p > 1) %>%
    ggplot(aes(x = pos, y = log10p)) +
    geom_hline(yintercept = c(10,15,20), color = "lightgrey") +
    geom_point(aes(color = chr, fill = chr)) +
    geom_hline(yintercept = FDRthreshold, color = "black", linetype = 2,
               size = 1) +
    facet_wrap(~ chr, nrow = 1, scales = "free_x",
               strip.position = "bottom") +
    #scale_color_viridis(option = "B", end = 0.8, discrete = TRUE) +
    #scale_fill_viridis(option = "B", end = 0.8, discrete = TRUE) +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          panel.background = element_rect(fill=NA), legend.position = "none") +
    labs(x = "Chromosome", y = "-log10(p value)") +
    scale_x_continuous(expand = c(0.22, 0.22)) +
    scale_color_manual(values = rep(c("#1B0C42FF", "grey"),9), guide = FALSE)
   #scale_shape_manual(values = rep(c(21,22),9), guide = FALSE)
  theme_set(theme_poster)
  save_plot(paste0("Manhattan_TMPL_BIOMASS_5_PCs_FDR_", str_replace_all(Sys.time(), ":", "."),
                   ".png"),
            plot = ggmanobject1, base_aspect_ratio = 4, base_height = 3)
```

```{r}
gwas_data <- readRDS("GWAS_datatable_KBSM_GR50_3_PCs_.rds")
gwas_data[,FDR_adj := p.adjust(pvalue, method = "BH")]
FDRthreshhi <- gwas_data %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0.0501, 1)) %>%  # 5% FDR threshold currently.
    summarise(thresh = max(log10p))
  FDRthreshlo <- gwas_data %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0, 0.0499)) %>%  # 5% FDR threshold currently.
    summarise(thresh = min(log10p))
  if(FDRthreshhi$thresh[1] > 0 & FDRthreshlo$thresh[1] > 0){
    FDRthreshold = (FDRthreshhi$thresh[1] + FDRthreshlo$thresh[1])/2
  } else if(FDRthreshhi$thresh[1] > 0){
    FDRthreshold = FDRthreshhi$thresh[1]
  } else if(FDRthreshlo$thresh[1] > 0){
    FDRthreshold = FDRthreshlo$thresh[1]
  } else {
    FDRthreshold = NA
  }

  ggmanobject1 <- gwas_data %>%
    filter(log10p > 1) %>%
    ggplot(aes(x = pos, y = log10p)) +
    geom_hline(yintercept = c(10,15), color = "lightgrey") +
    geom_point(aes(color = chr, fill = chr)) +
    geom_hline(yintercept = FDRthreshold, color = "black", linetype = 2,
               size = 1) +
    facet_wrap(~ chr, nrow = 1, scales = "free_x",
               strip.position = "bottom") +
    #scale_color_viridis(option = "B", end = 0.8, discrete = TRUE) +
    #scale_fill_viridis(option = "B", end = 0.8, discrete = TRUE) +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          panel.background = element_rect(fill=NA), legend.position = "none") +
    labs(x = "Chromosome", y = "-log10(p value)") +
    scale_x_continuous(expand = c(0.22, 0.22)) +
    scale_color_manual(values = rep(c("#1B0C42FF", "grey"),9), guide = FALSE)
   #scale_shape_manual(values = rep(c(21,22),9), guide = FALSE)
  theme_set(theme_poster)
  save_plot(paste0("Manhattan_KBSM_GR50_3_PCs_FDR_", str_replace_all(Sys.time(), ":", "."),
                   ".png"),
            plot = ggmanobject1, base_aspect_ratio = 4, base_height = 3)
```

>>>>

library(scales)
show_col(viridis(2, option = "D", end = 0.8))

# 4X vs 8X for Jason

wb_pheno <- loadWorkbook(file.path("C:", "Users", "ahm543", "Dropbox",
                                   paste0("GWAS DOE Switchgrass, ",
                                          "Consolidated Data"),
                                   paste0("DOE_GWAS_Master Plant List.xlsx")))
lst_pheno <- readWorksheet(wb_pheno, sheet = getSheets(wb_pheno))
planting_2018 <- lst_pheno$`GWAS 2018 Master Plant List`

ploidyplot <- planting_2018 %>%
  left_join(metadata) %>%
   mutate(PLOIDY = ifelse(ACC == "AP13", "4X", PLOIDY)) %>%
   filter(!is.na(PLOIDY)) %>%
    mutate(GENETIC_SUBPOP = case_when(is.na(Genetic_subpop_50per) ~ "Unknown",
                                    Genetic_subpop_50per == "Eastcoast" ~ "Atlantic",
                                    Genetic_subpop_50per == "Texas" ~ "Gulf",
                                    TRUE ~ Genetic_subpop_50per),
         ECOTYPE = case_when(is.na(Ecotype) ~ "Unknown", 
                             Ecotype == "TX" ~ "Lowland",
                             Ecotype == "Texas" ~ "Lowland",
                             TRUE ~ Ecotype))

ploidyplot$PLOIDY <- factor(ploidyplot$PLOIDY, levels = c("8X", "4X"))
ploidyplot$SITE <- factor(ploidyplot$SITE, levels = c("BRKG", "KBSM", "FRMI", "LINC", "CLMB", "STIL", "OVTN", "TMPL", "PKLE", "KING"))
ploidyplot$GENETIC_SUBPOP <- factor(ploidyplot$GENETIC_SUBPOP, levels = c("Midwest", "Atlantic", "Gulf", "Admixed", "Unknown"))
ploidyplot$ECOTYPE <- factor(ploidyplot$ECOTYPE, levels = c("Upland", "Coastal", "Lowland", "Unknown"))

ploidyplot %>%
  #group_by(SITE, PLOIDY) %>% tally() %>%
   ggplot(aes(x = SITE)) + 
   geom_bar(aes(fill = PLOIDY)) +
   scale_fill_manual(values = c("black", "darkgreen")) + 
  xlab("Sites (North to South)") + ylab("Number of Plants") + 
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 45, hjust = 1))

save_plot(filename = "Ploidy of Plants at Common Garden Sites.png", plot = last_plot())

ploidyplot %>%
  #group_by(SITE, PLOIDY) %>% tally() %>%
   ggplot(aes(x = SITE)) + 
   geom_bar(aes(fill = GENETIC_SUBPOP)) +
   scale_fill_manual(values = c("darkblue", "orange", "red", "grey", "lightgrey")) + 
  xlab("Sites (North to South)") + ylab("Number of Plants") + 
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 45, hjust = 1))

save_plot(filename = "Ploidy of Plants at Common Garden Sites.png", plot = last_plot())

@@

theme_set(theme_poster)
frzlostplot <- frz_freq %>%
  filter(Loss_BRKG > 159 | Loss_LINC > 179 | Loss_FRMI > 84 | 
           Loss_CLMB > 94) %>%
  mutate(Loss_freq = (Loss_BRKG/MAC_BRKG_2018 + Loss_FRMI/MAC_FRMI_2018 +
                            Loss_LINC/MAC_LINC_2018 +
                            Loss_CLMB/MAC_CLMB_2018)/4) %>% 
  filter(Loss_freq > 0.42) %>%
  ggplot(aes(x = POS/1000000, y = Loss_freq)) +
  geom_point(aes(color = CHR), alpha = 0.35) + 
  facet_wrap(~CHR, scales = "free_x", nrow = 1,
            strip.position = "bottom") + 
  #scale_fill_viridis(trans = "log10", option = "B") + 
  xlab("Chromosome") + ylab("Fraction of Minor Allele Lost") +
    scale_x_continuous(expand = c(0.03, 0.03)) +
  theme(legend.position = "none", 
        axis.text.x = element_blank(),
          axis.ticks.x = element_blank()) +
        #axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = c(rep(c("#1B0C42FF", "grey"), 9)))

save_plot(filename = paste0("Distribution_of_SNPs_1per_delta_all_four_sites_lost_50per", str_replace_all(Sys.time(), ":", "."),
                   ".png"), plot = frzlostplot, base_asp = 4, base_height = 4)

@@

# Manhattan plots for GR50 in KBSM and biomass in TMPL
```{r}
gwas_data <- readRDS("GWAS_datatable_TMPL_BIOMASS_5_PCs.rds")
gwas_data[,FDR_adj := p.adjust(pvalue, method = "BH")]
FDRthreshhi <- gwas_data %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0.1001, 1)) %>%  # 5% FDR threshold currently.
    summarise(thresh = max(log10p))
  FDRthreshlo <- gwas_data %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0, 0.0999)) %>%  # 5% FDR threshold currently.
    summarise(thresh = min(log10p))
  if(FDRthreshhi$thresh[1] > 0 & FDRthreshlo$thresh[1] > 0){
    FDRthreshold = (FDRthreshhi$thresh[1] + FDRthreshlo$thresh[1])/2
  } else if(FDRthreshhi$thresh[1] > 0){
    FDRthreshold = FDRthreshhi$thresh[1]
  } else if(FDRthreshlo$thresh[1] > 0){g
    FDRthreshold = FDRthreshlo$thresh[1]
  } else {
    FDRthreshold = NA
  }

  ggmanobject1 <- gwas_data %>%
    filter(log10p > 1) %>%
    ggplot(aes(x = pos, y = log10p)) +
    geom_hline(yintercept = c(10,15,20), color = "lightgrey") +
    geom_point(aes(color = chr, fill = chr)) +
    geom_point(aes(color = chr, fill = chr)) +
    #geom_hline(yintercept = FDRthreshold, color = "black", linetype = 2,
    #           size = 0.7) +
    geom_hline(yintercept = bonferroni, color = "#FAC127FF", linetype = 2,
               size = 1) +
    facet_wrap(~ chr, nrow = 1, scales = "free_x",
               strip.position = "bottom") +
    #scale_color_viridis(option = "B", end = 0.8, discrete = TRUE) +
    #scale_fill_viridis(option = "B", end = 0.8, discrete = TRUE) +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          panel.background = element_rect(fill=NA), legend.position = "none") +
    labs(x = "Chromosome", y = "-log10(p value)") +
    scale_x_continuous(expand = c(0.18, 0.18)) +
    scale_color_manual(values = rep(c("#1B0C42FF", "grey"),9), guide = FALSE)
   #scale_shape_manual(values = rep(c(21,22),9), guide = FALSE)
  theme_set(theme_poster)
  save_plot(paste0("Manhattan_TMPL_BIOMASS_5_PCs_FDR_", str_replace_all(Sys.time(), ":", "."),
                   ".png"),
            plot = ggmanobject1, base_aspect_ratio = 4, base_height = 4)
```

```{r}
gwas_data2 <- readRDS("GWAS_datatable_KBSM_GR50_3_PCs_.rds")
gwas_data2[,FDR_adj := p.adjust(pvalue, method = "BH")]
FDRthreshhi <- gwas_data2 %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0.1001, 1)) %>%  # 5% FDR threshold currently.
    summarise(thresh = max(log10p))
  FDRthreshlo <- gwas_data2 %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0, 0.0999)) %>%  # 5% FDR threshold currently.
    summarise(thresh = min(log10p))
  if(FDRthreshhi$thresh[1] > 0 & FDRthreshlo$thresh[1] > 0){
    FDRthreshold = (FDRthreshhi$thresh[1] + FDRthreshlo$thresh[1])/2
  } else if(FDRthreshhi$thresh[1] > 0){
    FDRthreshold = FDRthreshhi$thresh[1]
  } else if(FDRthreshlo$thresh[1] > 0){
    FDRthreshold = FDRthreshlo$thresh[1]
  } else {
    FDRthreshold = NA
  }

  ggmanobject1 <- gwas_data2 %>%
    filter(log10p > 1) %>%
    ggplot(aes(x = pos, y = log10p)) +
    geom_hline(yintercept = c(10,15), color = "lightgrey") +
    geom_point(aes(color = chr, fill = chr)) +
    #geom_hline(yintercept = FDRthreshold, color = "black", linetype = 2,
    #           size = 0.7) +
    geom_hline(yintercept = bonferroni, color = "#FAC127FF", linetype = 2,
               size = 1) +
    facet_wrap(~ chr, nrow = 1, scales = "free_x",
               strip.position = "bottom") +
    #scale_color_viridis(option = "B", end = 0.8, discrete = TRUE) +
    #scale_fill_viridis(option = "B", end = 0.8, discrete = TRUE) +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          panel.background = element_rect(fill=NA), legend.position = "none") +
    labs(x = "Chromosome", y = "-log10(p value)") +
    scale_x_continuous(expand = c(0.18, 0.18)) +
    scale_color_manual(values = rep(c("#1B0C42FF", "grey"),9), guide = FALSE)
   #scale_shape_manual(values = rep(c(21,22),9), guide = FALSE)
  theme_set(theme_poster)
  save_plot(paste0("Manhattan_KBSM_GR50_3_PCs_FDR_", str_replace_all(Sys.time(), ":", "."),
                   ".png"),
            plot = ggmanobject1, base_aspect_ratio = 4, base_height = 4)
```

# Manhattan plots for ASV's with 10% FDR & Bonferroni
```{r}
asvs <- c("ASV89_2_PCs", "ASV113_3_PCs", "ASV1197_3_PCs")
for(i in seq_along(asvs)){
gwas_data <- readRDS(paste0("../GWAS_datatable_", asvs[i], "_.rds"))
#gwas_data[,FDR_adj := p.adjust(pvalue, method = "BH")]
FDRthreshhi <- gwas_data %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0.1001, 1)) %>%  # 5% FDR threshold currently.
    summarise(thresh = max(log10p))
  FDRthreshlo <- gwas_data %>%
    as_tibble() %>%
    filter(between(FDR_adj, 0, 0.0999)) %>%  # 5% FDR threshold currently.
    summarise(thresh = min(log10p))
  if(FDRthreshhi$thresh[1] > 0 & FDRthreshlo$thresh[1] > 0){
    FDRthreshold = (FDRthreshhi$thresh[1] + FDRthreshlo$thresh[1])/2
  } else if(FDRthreshhi$thresh[1] > 0){
    FDRthreshold = FDRthreshhi$thresh[1]
  } else if(FDRthreshlo$thresh[1] > 0){g
    FDRthreshold = FDRthreshlo$thresh[1]
  } else {
    FDRthreshold = NA
  }

  ggmanobject1 <- gwas_data %>%
    filter(log10p > 1) %>%
    ggplot(aes(x = pos, y = log10p)) +
    geom_hline(yintercept = c(10,15), color = "lightgrey") +
    geom_point(aes(color = chr, fill = chr)) +
    geom_point(aes(color = chr, fill = chr)) +
    geom_hline(yintercept = FDRthreshold, color = "black", linetype = 2,
               size = 0.7) +
    geom_hline(yintercept = bonferroni, color = "#FAC127FF", linetype = 2,
               size = 1) +
    facet_wrap(~ chr, nrow = 1, scales = "free_x",
               strip.position = "bottom") +
    #scale_color_viridis(option = "B", end = 0.8, discrete = TRUE) +
    #scale_fill_viridis(option = "B", end = 0.8, discrete = TRUE) +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          panel.background = element_rect(fill=NA), legend.position = "none") +
    labs(x = "Chromosome", y = "-log10(p value)") +
    scale_x_continuous(expand = c(0.18, 0.18)) +
    scale_color_manual(values = rep(c("#1B0C42FF", "grey"),9), guide = FALSE)
   #scale_shape_manual(values = rep(c(21,22),9), guide = FALSE)
  theme_set(theme_poster)
  save_plot(paste0("../../presentations/Nice_Manhattans/Manhattan_", asvs[i], "_Bonferroni_10percent_FDR_", str_replace_all(Sys.time(), ":", "."),
                   ".png"),
            plot = ggmanobject1, base_aspect_ratio = 4, base_height = 4)
}
```
